% Cover letter using letter.cls
\documentclass{letter}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8in    % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Dustin Withers}                  % name for signature 
\longindentation=0pt                     % needed to get closing flush left
\let\raggedleft\raggedright              % needed to get date flush left
 
\begin{letter}{Brenda Smith \\
Special Collections \\
Rare Imprints Cataloger, \\
\& Technical Contact at the \\
Kentucky Historical Society \\
(502) 564-1792 x4484 or x4470 \\
brendaj.smith@ky.gov} 

\begin{center}
{\large\bf Dustin Withers} \\
{8158 Bonnafair Dr. \\ Hermitage, TN 37076  \\ (615) 482-2167} 
\end{center} \vfill % forces letterhead to top of page
 

\opening{Dear Ms. Smith:}
 
\noindent I would like to apply for the Database Administrator position that is available. I heard about the position from Sarah Milligan who currently works at the Kentucky Historical Society and is a close personal friend.
 
\noindent The position looks to be a good fit for my set of skills. I have over 5 years of experience managing databases and building database backed applications. I'm currently employed at Griffin Technology as the IT Manager. My duties there include managing an Oracle 10G database that supports the companies main accounting and finance application, JD Edwards. I also manage critical projects and utilize a team of 5 other IT professionals to schedule and complete those projects. During my time there I've managed and deployed many different databases on multiple operating systems. On my off time I run a small Web Development company that develops content management systems for various clients including small to large businesses and individuals.
 
\noindent I would like to request an interview at your earliest convenience. I'm available by phone at 615-482-2167. My email address is fadeddata@gmail.com. As I am only a few hours away I can also be available for an in person interview. Thank you for your time and consideration.
 
\closing{Sincerely yours,}

  


\end{letter}
 

\end{document}












